\section{Additional Experimental Results}
\label{app:results}

\new{\subsection{Surveyed Audio-Native Models}\label{app:audio-native-audit}}

\new{\tauvoice{} evaluates three audio-native models in the main body (\S\ref{sec:experiments}); this appendix documents the broader survey behind that selection. As of March 2026, we surveyed the audio-native models listed in Table~\ref{tab:audio-native-audit}. The two inclusion criteria are realtime full-duplex audio \emph{and} native tool calling, both required because \tauvoice{} is a grounded, tool-use benchmark; the disqualified models satisfy the first criterion but not the second, since their published documentation does not describe tool-calling support from their audio-conditioned head. Amazon Nova 2 Sonic qualifies on both axes but was deprioritized as another closed-source provider unlikely to add qualitatively different insight to the three already evaluated. The audio-native landscape evolves quickly; the live leaderboard at \href{https://taubench.com}{taubench.com} tracks the canonical up-to-date list.}\why{addresses macs W4 + follow-up; vw95 W3}

\begin{table}[h]
\caption{\new{Audio-native models surveyed for \tauvoice{} evaluation, as of March 2026. Realtime full-duplex audio = streaming bidirectional audio with voice-activity-detected turn-taking. Native tool calling = the model supports tool calls directly from its audio-conditioned head, without an external ASR$\to$LLM cascade. Both criteria are required for inclusion (\S\ref{sec:experiments}). The audio-native landscape evolves quickly; the live leaderboard at \href{https://taubench.com}{taubench.com} tracks the canonical up-to-date list.}\why{addresses macs W4}}
\label{tab:audio-native-audit}
\centering
\begin{small}
\resizebox{\columnwidth}{!}{%
\new{\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Model} & \makecell{\textbf{Realtime}\\\textbf{full-duplex audio}} & \makecell{\textbf{Native}\\\textbf{tool calling}} & \makecell{\textbf{Evaluated}\\\textbf{in \tauvoice{}}} \\
\midrule
\multicolumn{4}{l}{\textit{Qualifying (both criteria satisfied)}} \\
OpenAI Realtime~\cite{openai_introducing_2025} & \checkmark & \checkmark & \checkmark \\
Gemini Live~\cite{vertex_ai_gemini_2025} & \checkmark & \checkmark & \checkmark \\
xAI Voice Agent~\cite{xai_grok_voice_2025} & \checkmark & \checkmark & \checkmark \\
Amazon Nova 2 Sonic~\cite{amazon_nova_sonic_2025} & \checkmark & \checkmark & \xmark$^{\dagger}$ \\
\midrule
\multicolumn{4}{l}{\textit{Realtime full-duplex audio, but no native tool calling}} \\
NTPP~\cite{wang_ntpp_2025} & \checkmark & \xmark & \xmark \\
LLaMA-Omni~\cite{fang_llama-omni_2025} & \checkmark & \xmark & \xmark \\
SALMONN-omni~\cite{yu_salmonn-omni_2025} & \checkmark & \xmark & \xmark \\
Moshi~\cite{defossez_moshi_2024} & \checkmark & \xmark & \xmark \\
PersonaPlex~\cite{nvidia_personaplex_2026} & \checkmark & \xmark & \xmark \\
MiniCPM-o 4.5~\cite{openbmb_minicpm-o_2026} & \checkmark & \xmark & \xmark \\
Qwen-Omni-Realtime~\cite{qwen_omni_realtime_2025} & \checkmark & \xmark & \xmark \\
\bottomrule
\end{tabular}}%
}
\end{small}
\\[0.5em]
\new{\footnotesize $^{\dagger}$ Qualifies on both axes but deprioritized as another closed-source provider unlikely to add qualitatively different insight beyond the three already evaluated.}\why{addresses macs follow-up}
\end{table}

\subsection{Voice Interaction Quality: Full Metric Breakdown}
\label{app:voice-metrics-detail}

Table~\ref{tab:voice-quality-detail} provides the full breakdown of voice interaction metrics. Columns are grouped by: \textbf{Latency} ($L_R$ = Response Latency, $L_Y$ = Yield Latency), \textbf{Responsiveness} ($R_R$ = Response Rate, $R_Y$ = Yield Rate), \textbf{Interrupt} ($I_A$ = Agent Interruption Rate), and \textbf{Selectivity} ($S_{BC}$ = Backchannel Correct, $S_{VT}$ = Vocal Tic Correct, $S_{ND}$ = Non-Directed Correct). For $L_R$, $R_R$, and $I_A$, separate columns show Clean (C) and Realistic (R) speech conditions; other metrics are evaluated on Realistic only.

\begin{table*}[h]
\caption{Voice interaction quality metrics---full breakdown (Realistic condition). \textbf{Bold} indicates best per domain. $\uparrow$ = higher is better, $\downarrow$ = lower is better.}
\label{tab:voice-quality-detail}
\centering
\begin{small}
\resizebox{\textwidth}{!}{%
\input{results/full_voice_quality_table}
}
\end{small}
\end{table*}

% TODO: Add per-task breakdown, statistical significance tests


\subsection{Qualitative Error Analysis}
\label{app:qualitative-analysis}

We conducted a qualitative analysis of task failures to understand error sources and types. We annotated all failed simulations from two analysis cohorts: (1) Voice-Fragile (43 simulations across 20 tasks passing in text but failing in Clean audio), and (2) Noise-Fragile (48 simulations across 19 tasks passing in Clean but failing in Realistic audio).

\paragraph{Qualitative Annotations.}
Table~\ref{tab:full-notes-both} shows the qualitative annotations for each failed simulation.

\begin{table*}[h]
\caption{Qualitative error annotations for task completion failures. Left: Voice-Fragile cohort (43 simulations from Clean audio setting). Right: Noise-Fragile cohort (48 simulations from Realistic audio setting).}
\label{tab:full-notes-both}
\centering
\begin{small}
\begin{minipage}{0.48\textwidth}
\centering
\textbf{Voice-Fragile}\\[0.5em]
\input{results/full_notes_text_vs_clean_audio}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\centering
\textbf{Noise-Fragile}\\[0.5em]
\input{results/full_notes_clean_vs_realistic_audio}
\end{minipage}
\end{small}
\end{table*}

\paragraph{Error Type Definitions.}
We categorize errors into six types based on observed failure patterns:

\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{Logical} (Agent or User): Reasoning or execution errors, including incorrect tool call arguments/formatting, taking wrong actions (cancelling/modifying wrong items), failing to follow instructions (not asking for spelling, not confirming), or losing track of conversation state.
    
    \item \textbf{Transcription} (Agent): Speech-to-text errors where the agent incorrectly transcribes user speech, most commonly during authentication when users spell names/emails letter-by-letter, or when transcribing specific user requests.
    
    \item \textbf{Hallucination} (Agent or User): Agent fabricates information (e.g., inventing item IDs, hallucinating order details) or user simulator states information not present in the task instructions.
    
    \item \textbf{VAD/Unresponsive} (Agent): Voice Activity Detection errors where the agent fails to detect user speech, or agent goes silent for an extended period despite multiple user check-ins.
    
    \item \textbf{Timeout} (Agent): Agent could not resolve the call within the 10-minute simulation limit, typically due to being too slow or verbose.
    
    \item \textbf{Early Termination} (User): User ends the call prematurely before the task is fully completed, often due to ambiguous communication where user assumes the task is done when it is not.
\end{itemize}

\new{\subsection{Commonsense vs.\ Policy Error Taxonomy}\label{app:commonsense-taxonomy}}

\new{The error-type taxonomy in \S\ref{app:qualitative-analysis} (logical / transcription / hallucination / VAD-unresponsive / timeout / early-termination) categorizes failures by their \emph{mechanical surface form}. This appendix presents a complementary cut of the same 91 failed simulations along an orthogonal axis: the \emph{skill that would be required to succeed}. We focus on the 68 agent-attributable failures (the union of agent-side errors across both cohorts), since user-simulator failures are not informative about the agent's commonsense ability. The motivating question is whether the failures \tauvoice{} surfaces reflect domain-specific policy knowledge (which a generic LLM would not be expected to possess) or domain-agnostic commonsense conversational skills (which any competent voice conversation requires). Table~\ref{tab:commonsense-taxonomy} summarizes the breakdown.}\why{addresses vw95 W2; macs final framing}

\begin{table}[h]
\caption{\new{Re-categorization of the 68 agent-attributable failures (across both Voice-Fragile and Noise-Fragile cohorts) by the skill required to succeed. Buckets are mutually exclusive; each failure is assigned to the single skill whose absence is the proximal cause of the agent error. Only 7\% require domain-specific policy knowledge; 93\% reflect domain-agnostic commonsense conversational skills.}\why{addresses vw95 W2}}
\label{tab:commonsense-taxonomy}
\centering
\begin{small}
\new{\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Skill required to succeed} & \textbf{Count} & \textbf{\%} \\
\midrule
\multicolumn{3}{l}{\textit{Domain-specific}} \\
Policy knowledge (retail/airline/telecom rules) & 5 & 7\% \\
\midrule
\multicolumn{3}{l}{\textit{Domain-agnostic commonsense}} \\
Spelling (names, emails, IDs over audio) & 26 & 38\% \\
Conversational grounding (confirm before irreversible actions) & 15 & 22\% \\
Conversational honesty (do not claim un-executed actions) & 16 & 24\% \\
Multi-part request tracking & 4 & 6\% \\
Arithmetic / self-consistency & 2 & 3\% \\
\midrule
\textbf{Total} & \textbf{68} & \textbf{100\%} \\
\bottomrule
\end{tabular}}
\end{small}
\end{table}

\new{\paragraph{Bucket definitions.}}\why{addresses vw95 W2}

\new{\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{Policy knowledge} (5/68): Failure requires knowledge of a domain-specific rule documented in the agent's policy prompt (e.g., a retail rule about same-item exchange, an airline rule about baggage allowance tiers, a telecom rule about line-suspension eligibility). These are the failures a generic LLM would not be expected to handle without the policy.

    \item \textbf{Spelling} (26/68): Agent transcribes a spelled-out name, email, or order ID incorrectly, blocking authentication or producing a downstream lookup miss. Verifiable from the database state: the spelled string never matches a user record.

    \item \textbf{Conversational grounding} (15/68): Agent executes an irreversible action (refund, cancellation, address change, line suspension) without explicit user confirmation, or fails to surface information the user needs to make the next decision (e.g., refund amount, replacement availability). Verifiable from the tool-call log against the user instructions.

    \item \textbf{Conversational honesty} (16/68): Agent claims to the user that an action was performed when no corresponding tool call exists in the trace. Verifiable from the tool-call log: the asserted action has no matching invocation.

    \item \textbf{Multi-part request tracking} (4/68): User makes a compound request (e.g., ``cancel order X and also update my address''); agent completes one part and treats the call as resolved. Verifiable from the final database state vs.\ the gold target.

    \item \textbf{Arithmetic / self-consistency} (2/68): Agent makes an arithmetic error (refund total, line-item sum) or contradicts an earlier statement in the same call. Verifiable from the dialogue trace.
\end{itemize}}\why{addresses vw95 W2}

\new{\paragraph{Interpretation.} The 93\%/7\% split provides empirical evidence that \tauvoice{} primarily measures domain-agnostic commonsense conversational ability through the task lens, not domain-specific policy lookup. Spelling, grounding, and honesty---the three largest buckets---are not retail-, airline-, or telecom-specific skills; they are properties of competent voice interaction in any setting. We agree with reviewer vw95 that dedicated commonsense probes (independent of grounded tasks) would be a valuable complement, and we note this as future work in \S\ref{sec:conclusion}.}\why{addresses vw95 W2}

\new{\paragraph{Reproducibility note.} The bucket assignments were produced by re-coding the qualitative annotations from \S\ref{app:qualitative-analysis} (Table~\ref{tab:full-notes-both}) along the skill-required axis. A single failure can in principle exhibit more than one missing skill; we assign each to the single skill whose absence is the proximal cause, which matches the convention used for the mechanical error-type taxonomy in \S\ref{app:qualitative-analysis}. The underlying per-simulation annotations are reported in Table~\ref{tab:full-notes-both}; the re-coding from mechanical error type to skill-required bucket is mechanical (a fixed mapping plus a single ambiguous-case rule), and the resulting counts are the ones reported in Table~\ref{tab:commonsense-taxonomy}.}\why{addresses vw95 W2}

\new{\subsection{Simulator Realism Validation}\label{app:simulator-realism}}

\new{To validate that the voice user simulator produces interactions that resemble realistic caller behavior, we conducted a small human annotation study.}\why{addresses macs Q3/Q4}

\new{\paragraph{Methodology.} Two annotators independently rated 60 simulations drawn from the benchmark on a 1--4 Likert scale (1 = clearly unrealistic, 4 = indistinguishable from a real caller). Each simulation was rated along six dimensions:}\why{addresses macs Q3/Q4}

\new{\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{Voice prosody}: pitch, rhythm, and intonation of the synthesized caller speech.
    \item \textbf{Audio environment realism}: plausibility of the simulated background audio (noise, ambient sounds, intermittent events).
    \item \textbf{Turn-taking naturalness}: timing and flow of speaker transitions.
    \item \textbf{Backchannel naturalness}: realism of acknowledgement tokens (``mm-hmm'', ``okay'').
    \item \textbf{Interruption behavior}: appropriateness and frequency of mid-utterance interjections.
    \item \textbf{Behavioral plausibility}: holistic judgment of whether the caller behaves like a real human across the whole call.
\end{itemize}}\why{addresses macs Q3/Q4}
\todo{verify with Victor: were the 60 simulations stratified across domains $\times$ speech-complexity conditions, or sampled uniformly? Current neutral phrasing avoids overclaiming.}

\new{\paragraph{Results.} Table~\ref{tab:simulator-realism} reports the per-dimension means averaged across the two annotators. Averaging across the six dimensions, the simulator achieves an overall mean of 3.1/4, with 83\% of all individual ratings at 3 or above. Within-1 inter-rater agreement --- the fraction of (simulation, dimension) pairs on which the two raters' scores are within one point of each other --- is 94\%, suggesting consistent perception of simulator quality across annotators.}\why{addresses macs Q3/Q4}

\begin{table}[h]
\caption{\new{Simulator realism ratings, averaged across two annotators on 60 simulations (1--4 scale; higher is better). Overall row is the mean across the six dimensions.}\why{addresses macs Q3/Q4}}
\label{tab:simulator-realism}
\centering
\begin{small}
\new{\begin{tabular}{@{}lc@{}}
\toprule
\textbf{Dimension} & \textbf{Mean rating} \\
\midrule
Voice prosody & 2.6 / 4 \\
Audio environment realism & 3.3 / 4 \\
Turn-taking naturalness & 3.1 / 4 \\
Backchannel naturalness & \textbf{3.5 / 4} \\
Interruption behavior & 3.0 / 4 \\
Behavioral plausibility (holistic) & 3.1 / 4 \\
\midrule
\textbf{Overall (mean across dimensions)} & \textbf{3.1 / 4} \\
\bottomrule
\end{tabular}}
\end{small}
\end{table}

\new{\paragraph{Discussion.} The dimensions most directly relevant to task evaluation---turn-taking, interruption behavior, backchanneling, and overall behavioral plausibility---all score at or above 3.0/4, supporting the use of the simulator as a controllable substitute for human callers in this benchmark. The weakest dimension is voice prosody (2.6/4), consistent with our deliberate choice (\S\ref{sec:conclusion}) not to evaluate agent speech generation quality and to treat TTS-synthesized caller audio as indicative rather than definitive. This study is not a substitute for evaluation with real human callers, which we list as future work (\S\ref{sec:conclusion}); rather, it provides a check that the dimensions of simulator behavior that most directly affect agent task completion are acceptably realistic.}\why{addresses macs Q3/Q4}

\subsection{Statistical Reliability Analysis}
\label{app:stat-sig}

\new{To assess statistical reliability, we conducted 2 independent runs per condition across all three domains (Airline $n=50$, Retail $n=114$, Telecom $n=114$). We use paired permutation tests rather than trial-level confidence intervals: for each pair of conditions, we compute per-task mean success rates, pair observations by task ID, and test whether the paired differences are systematically non-zero (100k permutations, two-sided). $p$-values are Holm-Bonferroni corrected within each (domain, model) group to control for multiple comparisons; for the combined view, correction is applied within each model across all comparisons. Because rates are pooled across both runs, they may differ slightly from the single-run rates reported in the main results.}\why{addresses beyN W4/Q5}\old{To assess statistical reliability, we conducted 2 independent runs per condition on the Retail domain (n=114 tasks per run, 228 simulations per condition). We use paired permutation tests rather than trial-level confidence intervals: for each pair of conditions, we compute per-task mean success rates, pair observations by task ID (114 paired observations), and test whether the paired differences are systematically non-zero (100k permutations, two-sided). P-values are Holm-Bonferroni corrected within each provider group to control for multiple comparisons. Because rates are pooled across both runs, they may differ slightly from the single-run rates reported in the main results.}

\new{Two patterns hold across all three domains (Tables~\ref{tab:stat-sig} and~\ref{tab:stat-sig-per-domain}). First, the gap between voice and reasoning-text (GPT-5) is large and significant in every domain and for every model (all $p < 0.001$). Second, the Clean-to-Realistic degradation holds in Retail for all models, but in Airline and Telecom it is only significant for \texttt{grok-voice}. The most notable per-domain deviation is in Telecom, where \texttt{grok-voice}'s Clean rate (57.5\%) significantly \emph{exceeds} the non-reasoning text baseline ($+$20.6pp, $p < 0.001$); this pulls the combined non-reasoning Text$\,\to\,$Clean gap for \texttt{grok-voice} to non-significance ($p = 0.231$), but the anomaly disappears under Realistic conditions where Text$\,\to\,$Realistic is significant for all three models.}\why{addresses beyN W4/Q5}\old{Table~\ref{tab:stat-sig} confirms that both key gaps are statistically significant: (1) the text-to-Clean gap---all providers show significant drops from both text baselines ($p < 0.05$), including the narrowest gap between GPT-4.1 (76.3\%) and OpenAI Clean (67.5\%, $\Delta = -8.8$pp, $p = 0.032$); and (2) the Clean-to-Realistic gap---all three providers show significant degradation (Google $\Delta = -13.2$pp, $p = 0.026$; OpenAI $\Delta = -24.6$pp, $p < 0.001$; xAI $\Delta = -13.2$pp, $p = 0.044$).}

\old{Under Clean conditions, OpenAI (67.5\%) is clearly separated from xAI (50.0\%) and Google (42.1\%). Under Realistic conditions, OpenAI remains strongest (43.0\%), followed by xAI (36.8\%) and Google (28.9\%). The full set of pairwise comparisons across all five speech complexity conditions (Clean, Audio-only, Accents-only, Behavior-only, and Realistic) is available in the supplementary materials.}

\begin{table}[h]
\caption{\new{Pairwise statistical significance pooled across all three domains (Airline, Retail, Telecom; 2 runs each). Text (NR) = GPT-4.1; Text (R) = GPT-5. All $p$-values are Holm-Bonferroni corrected paired permutation tests (100k permutations, paired by task ID).}\why{addresses beyN W4/Q5}\old{Pairwise statistical significance for Retail domain (2 runs, n=114 tasks each). Text (NR) = GPT-4.1; Text (R) = GPT-5. All $p$-values are Holm-Bonferroni corrected paired permutation tests.}}
\label{tab:stat-sig}
\centering
\begin{small}
\input{results/stat_sig_table}
\end{small}
\end{table}

\begin{table}[h]
\caption{\new{Per-domain pairwise statistical significance (2 runs per condition). Text (NR) = GPT-4.1; Text (R) = GPT-5. All $p$-values are Holm-Bonferroni corrected paired permutation tests (100k permutations, paired by task ID, corrected within each (domain, model) group).}\why{addresses beyN W4/Q5}}
\label{tab:stat-sig-per-domain}
\centering
\begin{small}
\input{results/stat_sig_table_per_domain}
\end{small}
\end{table}

\new{\subsection{ASR-enabled Evaluation}\label{app:asr-enabled}}

\todo{Add ASR-enabled appendix content: full results of running the benchmark with the user simulator perceiving the agent's speech through ASR. Should report (i) the ASR pipeline used, (ii) the per-condition task-completion scores, (iii) the paired permutation test against the default configuration, and (iv) confirmation that the text-to-voice gap and the clean-to-realistic gap both remain statistically significant. (addresses beyN follow-up and vw95 follow-up.)}
